---
  title: "Methods and Results"
  author: 
  date: "`r Sys.Date()`"
  bibliography: refs.bib
  csl: pnas.csl
  output: 
    bookdown::word_document2:
      toc: no
      toc_depth: 6
      number_sections: true
      reference_docx: template.docx
    bookdown::html_document2:
      code_folding: hide
      number_sections: no
      toc: yes
      toc_depth: 6
      toc_float: yes
  editor_options: 
    chunk_output_type: console
---
```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
  ## numbers >= 10^5 will be denoted in scientific notation,      ## numbers >= 10^5 will be denoted in scientific notation,
    ## and rounded to 2 digits      ## and rounded to 2 digits
    options(digits = 2)
```

```{r loadpackages, echo = FALSE, results = "hide"}
  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR)

```
```{r loaddata, echo = FALSE, results = "hide"}
  # Tree
      data <- read.csv("./data/meta_data.csv")
      data <- data %>% 
              mutate(species2 = species)
  
  # Bring in and prune tree
       tree <- read.tree("./phylogeny/tree")
       tree$tip.label <- gsub("_", " ", tree$tip.label)
  phylogeny <- vcv(tree, corr=TRUE)

  # Summary statistics for the results
  inverts <- data %>% 
             mutate(insect = ifelse(class %in% c("Insecta", "Gastropoda", "Malacostraca", "Arachnida", "Clitellata (Phylum Annelida)",  "Secernentea (Phylum Nematoda)"), 1,0))

  parity <- data %>% group_by(species) %>% summarise(parity = unique(Gestation)) %>% group_by(parity) %>% summarise(n=n())

# Models
  model <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|variable, ~1|species), test = "t", data = data)

  I2(model, v = data$v_SMDH, phylo = FALSE)

  model <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|variable, ~1|species, ~1|species2), R = list(species = phylogeny), test = "t", data = data)

  model <- rma.mv(SMDH ~ SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)

  model <- rma.mv(SMDH ~ Harm_type-1, V = data$v_SMDH, random = list(~1|study, ~1|species, ~1|obs), R = list(species = phylogeny), test = "t", data = data)
  robust(model, cluster = data$study)

  model <- rma.mv(SMDH ~ Harm_type + SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
  robust(model, cluster = data$study)

  model <- rma.mv(SMDH ~ Gestation + SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
  robust(model, cluster = data$study)

  # Note that for gestation, these data on viviparous species are restricted completely to fish only, and indirect measurements. So, confounded. It's hard to know what is the driving factor...could be parity mode, but could be also due to all being fish, or even just that they are indirect measures, also, only 7 studies.

## Have a look at SSD data in relation to the key moderators
  ggplot(data, aes(y = SSD_lnRR, x = Harm_type)) + geom_violin() + geom_point()
  ggplot(data, aes(y = SSD_lnRR, x = Gestation)) + geom_violin() + geom_point()

```

# Results

Overall, we collected effect sizes for a total of `r length(unique(data$species))` species from `r length(unique(data$study))` studies. Unsurprisingly, invertebrates (classes: Insecta, Gastropoda, Malacostraca, Arachnida, Clitellata and Secernentea) made up most of the data (`r (table(inverts$insect)[2] / sum(table(inverts$insect)))*100`%). We obtained `r table(data$Harm_type)[2]` effect sizes from manipulations on species that resulted in direct harm (e.g., XX), whereas `r table(data$Harm_type)[3]` effects came from studies on species that manipulated indirect harm to females (e.g., mating rate and harassment). A total of `r table(data$Harm_type)[1]` effect sizes were from experiment where females received both direct and indirect harm from male matings. 

Across all species, `r table(data$Gestation)[1]` effects were from `r parity[1,2]` oviparous species, and `r table(data$Gestation)[2]` effects were from `r parity[2,2]` viviparous species. Unfortunately, effect sizes from viviparous species were all take from studies on fish species with indirect male harm. As such, we analyzed only 'harm type' and an index of sexual size dimorphism.


